\begin{thebibliography}{1}
	%\textit{Basic Format for Books:}\\
	\bibitem{ref1} Alom, MZ., Rahman, MMS., Nasrin, MS., Taha, TM., Asari, VK. \textit{COVID-MTNet: COVID-19 Detection with Multi-Task Deep Learning Approaches.} arXiv:2004.03747, 2020.
	
	\bibitem{ref2} Yan, Q., Wang, B., Gong, D., et al. \textit{COVID-19 Chest CT Image Segmentation -- A Deep Convolutional Neural Network Solution.} arXiv:2004.10987, 2020.
	
	\bibitem{ref3} Ronneberger, O., Fischer, P., and Brox, T. \textit{U-net: Convolutional networks for biomedical image segmentation.} In MICCAI, pages 234–241. Springer, 2015. 2
	
	\bibitem{ref4} Kalluri, T., Varma, G., Chandraker, M., and Jawahar, CW. \textit{Universal semi-supervised semantic segmentation.} CoRR, abs/1811.10323, 2018.
	
	\bibitem{ref5} Misra, I., and van der Maaten, L.\textit{ Self-supervised learning of pretext-invariant representations.} arXiv preprint arXiv:1912.01991, 2019.
	
	\bibitem{ref6} Chen, T., Kornblith, S., Norouzi, M., and Hinton, G. \textit{A simple framework for contrastive learning of visual representations.} arXiv:2002.05709, 2020.
	
	\bibitem{ref7} Newell, A., Deng, J. \textit{How Useful is Self-Supervised Pretraining for Visual Tasks?} arXiv:2003.14323, 2020.
	
	\bibitem{ref8} Novosel, J., Viswanath, P., and Arsenali, B. \textit{Boosting Semantic Segmentation With Multi-Task Self-Supervised Learning for Autonomous Driving Applications.} In Proc. of NeurIPS - Workshops, pages 1–11, Vancouver, BC, Canada, Dec. 2019.
	
	\bibitem{ref9} Kahl, F. \textit{“Fine-grained segmentation networks: Self-supervised segmentation for improved long-term visual localization,”} in Proceedings of the IEEE International Conference on Computer Vision, 2019, pp. 31–41.
	
	\bibitem{ref10} Chang, YC., Yu, CJ., Chang, SC., et al. \textit{Pulmonary sequelae in convalescent patients after severe acute respiratory syndrome: evaluation with thin-section CT.} Radiology 2005; 236(3):1067-1075.
	
	\bibitem{ref11} Yang, R., Li, X., Liu, H., Zhen, Y., Zhang, X., Xiong, Q., et al. \textit{Chest CT Severity Score: An Imaging Tool for Assessing Severe COVID-19. Radiol Cardiothorac Imaging.} 2020;2(2):e200047.
	
	\bibitem{ref12} Shan, F., Gao, Y., Wang, J., Shi, W., Shi, N., Han, M., Xue, Z., and Shi, Y. \textit{Lung Infection Quantification of COVID-19 in CT Images with Deep Learning.} arXiv preprint arXiv:2003.04655, 1-19, 2020.

	\bibitem{ref13} Yan, Q., Wang, B., Gong D., et al. \textit{COVID-19 Chest CT Image Segmentation – A Deep Convolutional Neural Network Solution.} arXiv preprint arXiv:2004.10987, 2020.

	\bibitem{ref14} Fan, DP., Zhou, T., Ji, GP., et al. \textit{Inf-Net: Automatic COVID-19 Lung Infection Segmentation from CT Scans.} arXiv preprint arXiv:2004.14133v2, 2020.

	\bibitem{ref15} Alexander Kolesnikov, Xiaohua Zhai, and Lucas Beyer. \textit{Revisiting self-supervised visual representation learning.} In Conference on Computer Vision and Pattern Recognition (CVPR), 2019.

	\bibitem{ref16} Trinh, TH., Luong, MT., and Le, QV. \textit{Selfie: Self-supervised pretraining for image	embedding.} arXiv preprint arXiv:1906.02940, 2019.

	\bibitem{ref17} Frinken, V., Zamora-Martinez, F., Espana-Boquera, S., Castro-Bleda, M. J., Fischer, A., and Bunke, H. (2012). \textit{Long-short term memory neural networks language modeling for handwriting recognition.} In Pattern Recognition (ICPR), 2012 21st International Conference on, pages 701–704. IEEE.

	\bibitem{ref18}  LeCun, Y., Haffner, P., Bottou, L., and Bengio, Y. \textit{Object recognition with gradient-based learning.} In Shape, contour and grouping in computer vision, pages 319–345. 1999.

	\bibitem{ref19} Kingma, Diederik, P. and Welling, M. \textit{Auto-Encoding Variational Bayes.} In The 2nd International Conference on Learning Representations (ICLR), 2013.

	\bibitem{ref20}  Goodfellow IJ., Pouget-Abadie, J., Mirza, M., Xu, B., Warde-Farley, D., Ozair, S., Courville, AC., and Bengio, Y. \textit{Generative adversarial nets.} In Proceedings of NIPS, pages 2672– 2680, 2014.

	\bibitem{ref21} Zhao, JY., Zhang, YC., He, XH., Xie, PT. \textit{COVID-CT-Dataset: a CT scan dataset about COVID-19.} arXiv preprint arXiv: 2003.13865, 2020.

	\bibitem{ref22} Cohen, JP., Morrison, P., and Dao, L.  \textit{COVID-19 Image Data Collection.} arXiv preprint arXiv: 2003.11597, 2020. https://github.com/ieee8023/covid-chestxray-dataset.

	\bibitem{ref23} Ning, Lei, WS., Yang SJ., et al. (2020). \textit{iCTCF: an integrative resource of chest computed tomography images and clinical features of patients with COVID-19 pneumonia.} 10.21203/rs.3.rs-21834/v1.

	\bibitem{ref24} Zhang, K., Liu, XH., Shen, J., et al. \textit{Clinically Applicable AI System for Accurate Diagnosis, Quantitative Measurements and Prognosis of COVID-19 Pneumonia Using Computed Tomography.} DOI: 10.1016/j.cell.2020.04.045.
	
	\bibitem{ref25}  Singh, S., Batra, A., Pang, G., Torresani, L., Basu, S.,  Paluri, M., and Jawahar, C. V.  \textit{Self-supervised feature learning for semantic segmentation of
	overhead imagery.} In BMVC, 2018.

	\bibitem{ref26} \textit{COVID-19 CT segmentation dataset}. Retrieved from http://medicalsegmentation.com/covid19/.

\end{thebibliography}
